Measurement Bias from Address Aliasing

### 2014-11-20 paper.tex
Updated author data. Changed to utf8.
Update to ACM latex Housekeeping standard
Removed sub-headline.
Swaped first figure
Aligned number presision in graph

% Typeset for Transactions on Architecture and Code Optimization
% \documentclass[prodmode,acmtaco]{acmsmall}
\documentclass{acm_proc_article-sp}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usepackage{tikz}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{underscore}
\usepackage{url}
\usepackage{lmodern} % Much clearer text

@@

%\acmVolume{V}
%\acmNumber{N}
%\acmArticle{A}
%\acmYear{YYYY}
%\acmMonth{0}

@@

\subtitle{[Extended Abstract]
\titlenote{Just a test}}
\numberofauthors{2}

% names here
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
LARS KIRKHOLT MELHUS\\
       \affaddr{Norwegian University of Science and Technology}\\
       \affaddr{fix 1932 Wallamaloo Lane}\\
       \affaddr{fix Wallamaloo, New Zealand}\\
       \email{fix@corporation.com}
% 2nd. author
\alignauthor
RUNE ERLEND JENSEN\\
       \affaddr{Norwegian University of Science and Technology}\\
       \affaddr{fix P.O. Box 1212}\\
       \affaddr{fix Dublin, Ohio 43017-6221}\\
       \email{runeerle@idi.ntnu.no}
}

\date{19 November 2014}
%LARS KIRKHOLT MELHUS and RUNE ERLEND JENSEN
%  \affil{Norwegian University of Science and Technology}

@@

% Choose from classification tree http://www.acm.org/about/class/ccs98-html
\category{C.4}{Performance of Systems}{Measurement techniques; Performance attributes}

% Terms come from a fixed list of predefined terms
\terms{Measurement, Performance}

% Free to choose keywords, but must be in alphabetical order
\keywords{4K address aliasing, BLAS, heap allocators, measurement bias, memory disambiguation}

@@

\pgfplotstableread{bin/microkernel-nehalem.dat}{\tblmicrokernelnehalem}
\pgfplotstableread{bin/microkernel-ivybridge.dat}{\tblmicrokernelivybridge}
\begin{figure}[t]
  \begin{tikzpicture}
    \begin{axis}[
        title = Nehalem (HT),
        width = \textwidth/2.1,
        height = 4.5cm,
        xlabel = Bytes added to environment,
        ylabel = Cycles,
        font = \footnotesize,
        domain = 0:4096,
        xtick = {0,1024,...,4096},
        xmin = 0,
        xmax = 4096,
        cycle list name = exotic
      ]
      \addplot[ycomb] table[x expr = \thisrowno{0}*16, y = cycles:u] \tblmicrokernelnehalem ;
    \end{axis}
  \end{tikzpicture}
  \begin{tikzpicture}
    \begin{axis}[
        title = Ivy Bridge,
        width = \textwidth/2.1,
        height = 4.5cm,
        xlabel = Bytes added to environment,
        ylabel = Cycles,
        font = \footnotesize,
        domain = 0:4096,
        xtick = {0,1024,...,4096},
        xmin = 0,
        xmax = 4096,
        cycle list name = exotic
      ]
      \addplot[ycomb] table[x expr = \thisrowno{0}*16, y = cycles:u] \tblmicrokernelivybridge ;
    \end{axis}
  \end{tikzpicture}
  \caption{\label{fig:microkernel-all-archs}Microkernel experiment on the ``Nehalem'' and ``Ivy Bridge'' microarchitectures.}
\end{figure}

>>>>

% paper.tex
% ACM sigmetric format
% Author: L. K. Melhus and R. E. Jensen
\documentclass{acm_proc_article-sp}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usepackage{tikz}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{underscore}
\usepackage{url}
\usepackage{lmodern} % Much clearer text
\usepackage[utf8]{inputenc}

@@

\conferenceinfo{SIGMETRICS}{2015 Portland, Oregon USA}
\CopyrightYear{2015}
%\acmVolume{V}
%\acmNumber{N}
%\acmArticle{A}
%\acmYear{YYYY}
%\acmMonth{0}

@@

\numberofauthors{2}

% names here
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Lars Kirkholt Melhus\\
       \affaddr{Norwegian University of Science and Technology}\\
       \affaddr{Sem Sælands vei 9}\\
       \affaddr{7491 Trondheim, Norway}\\
       \email{lars.kirkholt.melhus@gmail.com}
% 2nd. author
\alignauthor
Rune Erlend Jensen\\
       \affaddr{Norwegian University of Science and Technology}\\
       \affaddr{Sem Sælands vei 9}\\
       \affaddr{7491 Trondheim, Norway}\\
       \email{runeerle@idi.ntnu.no}
}

\date{19 November 2014}

@@

% Choose from classification tree http://www.acm.org/about/class/ccs98-html
\category{C.4}{Performance of Systems}{Measurement techniques; Performance attributes}
\category{D.3.4}{Processors}{Optimization; Run-time environments}

% Terms come from a fixed list of predefined terms
\terms{Measurement, Performance}
% Free to choose keywords, but must be in alphabetical order
\keywords{4K address aliasing, BLAS, heap allocators, measurement bias, memory disambiguation, performance counters}

@@

\pgfplotstableread{bin/microkernel-nehalem.dat}{\tblmicrokernelnehalem}
\pgfplotstableread{bin/microkernel-ivybridge.dat}{\tblmicrokernelivybridge}
\begin{figure}[t]
  \begin{tikzpicture}
    \begin{axis}[
        title = Nehalem (HT),
        y tick label style={
        /pgf/number format/.cd,
            fixed,
            fixed zerofill,
            precision=1,
        /tikz/.cd
        },
        width = \textwidth/2.1,
        height = 4.5cm,
        xlabel = Bytes added to environment,
        ylabel = Cycles,
        font = \footnotesize,
        domain = 0:4096,
        xtick = {0,1024,...,4096},
        xmin = 0,
        xmax = 4096,
        cycle list name = exotic
      ]
      \addplot[ycomb] table[x expr = \thisrowno{0}*16, y = cycles:u] \tblmicrokernelnehalem ;
    \end{axis}
  \end{tikzpicture}
  \begin{tikzpicture}
    \begin{axis}[
        title = Ivy Bridge,
        y tick label style={
        /pgf/number format/.cd,
            fixed,
            fixed zerofill,
            precision=1,
        /tikz/.cd
        },
        width = \textwidth/2.1,
        height = 4.5cm,
        xlabel = Bytes added to environment,
        ylabel = Cycles,
        font = \footnotesize,
        domain = 0:4096,
        xtick = {0,1024,...,4096},
        xmin = 0,
        xmax = 4096,
        cycle list name = exotic
      ]
      \addplot[ycomb] table[x expr = \thisrowno{0}*16, y = cycles:u] \tblmicrokernelivybridge ;
    \end{axis}
  \end{tikzpicture}
  \caption{\label{fig:microkernel-all-archs}Microkernel experiment on the ``Nehalem'' and ``Ivy Bridge'' microarchitectures.}
\end{figure}
